MSF_Groupwork-NBA_shotlog

### 2016-10-11 MSFGroupwork-NBAHotHand.Rmd
Impact of Super Star Players

#

```{r}
# Find shooting percentage of each match

# Reshape the dataframe

@@

# find Feild Goal % of each indivudual player in that match

game[, "FG%"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG%"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```

>>>>

# Find shooting percentage of each match

```{r}
# Reshape the dataframe

@@

# Find Feild Goal Percentage of each indivudual player in that match

game[, "FG.percentage"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG.percentage"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```

# Impact of Super Star Players

```{r}

# Pick out 8 of the best players in that regular season and create a new subset. Analyse how shooting percentage of these players can influence the result of a match.

super.star.list <- c("lebron james", "james harden", "russell westbrook", "stephen curry", "anthony davis", "blake griffin", "klay thompson", "lamarcus aldridge") # players picked out
super.star <- game[game$player_name %in% super.star.list, c("player_name", "W", "FGA", "FG.percentage")] # create a subset for these players

ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W))

# Replace "W" and "L" with 1 and 0 respectively, 
super.star[, "W"] <- as.character(super.star[, "W"])
for (i in 1:nrow(super.star)) {
  if (super.star[i, "W"] == "W") super.star[i, "W"] <- 1
  if (super.star[i, "W"] == "L") super.star[i, "W"] <- 0
}
super.star[, "W"] <- as.numeric(super.star[, "W"])

# Correlation test
t.test(super.star[, "W"], super.star[, "FGA"]) # this makes no sense...

# Linear regression
summary(lm(W ~ player_name + FGA, data = super.star))
summary(lm(W ~ player_name + FG.percentage, data = super.star))
